\chapter{Experimental Section}
\section{Instrumentation}
$^1$H-NMR and $^{13}$C-NMR spectra were recorded using Varian VXR-300 NMR spectrometer (300~MHz for $^1$H and 75~MHz for $^{13}$C), the chemical shift reference used was that from the employed solvent. The following abbreviations were used: s for singlet, d for doublet, m for multiplet.
$^{31}$P-NMR spectra were recorded at 69~MHz for $^{31}$P (200~MHz for $^1$H) using \ce{H3PO4} as external standard and liquid nitrogen to regulate the temperature.


\section{Solvents and Reagents}
Dichloromethane (\ce{CH2Cl2}), tetramethylethylenediamine (TMEDA) and triethylamine (\ce{Et3N}) were refluxed on calcium hydride (\ce{CaH2}) and distilled before use.
Toluene was refluxed on sodium (\ce{Na}) and distilled just before use.
Cyclohexane and tetrahydrofuran (THF) were refluxed on potassium (\ce{K}) and distilled just before use.
Phosphorus trichloride (\ce{PCl3}) was distilled and degassed by one freeze-pump-thaw cycle just before use.
Dimethylformamide (DMF) was dried on molecular sieves and distilled before use.

\section{Procedures}
% masse molecolari:
% Deoxycholic acid \cmpd{da} 392.57  C24H40O4
% 3$\alpha$-acetyloxy-12$\alpha$-hydroxy-7-deoxy\-cholic acid methyl ester \cmpd{amda} 448.635 C27H44O5
% AcOMe C3H6O2 74.08 densità 0.932
% p-TsOH C7H8O3S 172.202
% TMEDA dens 0.775 116.2 
% 1-methoxynaphthalene density 1.09 158.1998
% iodine 253.81
% 2-iodo-1-methoxynaphthalene \cmpd{moni} 284.093
% bis(dibenzyl\-idene\-acetone)palladium (\ce{Pd(dba)2} 575.005
% CsF 151.9038551
% Dinaphtho[2,1-d:1',2'-f][1,3,2]dioxaphosphepin, 4-chloro-; (11bS)-4-Chlorodinaphtho[2,1-d:1',2'-f][1,3,2]dioxaphosphepin; (S)-(1,1'-Binaphthalene-2,2'-dioxy)chlorophosphine; (S)-1,1'-Binaphthalene-2,2'-diyl phosphorochloridite; (S)-Binol chlorophosphite; (SAx)-2-Chlorodinaphtho[2,1-d:1',2'-f][1,3,2]dioxaphosphepine  350.73 è come quello mio ma con i binaftili legati in posizione 1,1' e gli ossigeni in 2,2' \cmpd{clorofosfito}
%155512-02-0 C22 H16 O2  8-(1-methoxy-2-naphthalenyl)-2H-Naphtho[1,8-bc]furan lo schifo erroneo 312.36
% 1,1'-di\-hydroxy-2,2'-bi\-naphthalene \cmpd{dhn} 286.324
% \p-dimethylamino-piridine????? (DMAP) 122.1677
% (3$\alpha$,5$\beta$,12$\alpha$)-3-(acetyloxy)-12-[dinaphtho[1,2-d:2',1'-f][1,3,2]dioxaphosphepin-4-yloxy]-cholan-24-oic acid methyl ester \cmpd{legante} 762.909 C47H55O7P
% phosphorus trichloride \ce{PCl3} densità 1.574 peso 137.3328
% triethylamine \ce{Et3N} dens 0.7255 peso 101.19
%1-nitro\-cyclo\-hexene dens 1.127 mm 127.141
%phenylboronic acid 121.93
%[RhCl(C2H4)2]2 388.930


\subsection[3$\alpha$-acetyloxy-12$\alpha$-hydroxy-7-deoxy\-cholic acid methyl \\ester \cmpd+{amda}]{3$\alpha$-acetyloxy-12$\alpha$-hydroxy-7-deoxy\-cholic acid \\methyl ester \cmpd+{amda}}\label{sec:sperimentale-amda}
%problema più serio: dalla procedura avremmo dovuto metterci 0.6 mL cioè circa 16 mmol di acqua che dagli appunti non risulta... boh, non l'avremo messa.

7-Deoxycholic acid \cmpd{da}, 2.23~g, 5.68~mmol), methyl acetate (AcOMe, 70~mL, 65~g, 0.88~mol) and \p-toluenesulfonic acid (\p-TsOH,
 0.26~g, 1.5~mmol) were combined in a 250~mL Schlenk flask fitted with a reflux condenser. The reaction mixture was then heated at reflux for 27 hours with magnetic stirring. The reaction was monitored using TLC (di\-chloro\-methane:acetone 9:1) %ma perchéèéèéèè non scrivo i solventi usati negli appunti?? Anzi, l'ho scritto poi. 
 and using an aqueous 5~\% solution of perchloric acid (\ce{HClO4}) to reveal the spots. The reaction mixture was then poured in saturated aqueous bicarbonate (\ce{NaHCO3}, 30~mL) and %boh, si intuisce dagli appunti
 extracted with di\-chloro\-methane (\ce{CH2Cl2}, 4~$\times$~25~mL). The extracts were washed with brine, dried on sodium sulfate (\ce{Na2SO4}) overnight, filtered and the
solvent evaporated under reduced pressure. The crude product was then purified via column chromatography (silica, di\-chloro\-methane:acetone 9:1). 
The evaporation of the eluent yielded 3$\alpha$-acetyloxy-12$\alpha$-hydroxy-7-deoxy\-cholic acid methyl ester \cmpd{amda} as a white spongy solid (1.76~g, 3.92~mmol, yield 69~\%). $\mathbf{^{1}}$\textbf{H-NMR} (300~MHz, \ce{CDCl3}, Figure \ref{sp:amda}, $\delta$, ppm):  0.67 (s, 3H, CH$_3$); 0.90 (s, 3H, CH$_3$%o forse questo 18 e l'altro 19? 
); 0.96 (d, J = 5.8~Hz, 3H, 28-CH$_3$); 1.00-1.90 (m, 25H, 1, 2, 4, 5, 7, 8, 9, 10, 11, 14, 15, 16, 17, 20, 22, 29); 2.01 (s, 3H, 32-CH$_3$CO); 2.15-2.40 (m, 2H, 23-CH$_2$); 3.65 (s, 3H, 30-CH$_3$OCO); 3.98 (m, 1H, 12-CH); 4.69 (m, 1H, 3-CH). $\mathbf{^{13}}$\textbf{C-NMR} (75~MHz, \ce{CDCl3}, $\delta$, ppm):  174.7, 170.7, 74.4, 73.2, 51.6, 48.4, 47.5, 46.6, 42.0, 36.1, 35.2, 35.0, 34.2, 33.8, 32.3, 31.2, 31.0, 28.8, 27.6, 27.1, 26.6, 26.1, 23.7, 23.2, 21.6, 17.5, 12.9.

\subsection{2-iodo-1-methoxy\-naphthalene \cmpd+{moni}}\label{sec:sperimentale-moni}
Using a Luer-Lock glass syringe \n-butyl\-lithium (2.5~M in hexane, 7.6~mL, 19~mmol) was added dropwise over 15 min to a solution of tetramethylethylenediamine (TMEDA, 2.9~mL, 2.3~g, 19~mmol) in cyclohexane (4~mL) in a three necked flask under nitrogen atmosphere. A solution of 1-methoxy\-naphthalene \cmpd{mon}, 2.7~mL, 2.9~g, 19~mmol) %oi Leo hai cercato su wikipedia in olandese se è Luer-Lock o Luer-Lok? XD Secondo me è giusto Luer-Lok, però si trova anche Luer-Lock...
in cyclohexane (10~mL) was then slowly added using a dropping funnel while maintaining the inert atmosphere.
The reaction mixture was stirred for 2 hours then was cooled to \SI{0}{\celsius} and a solution of iodine (\ce{I2}, 8.54~g, 33.7~mmol) in tetrahydrofuran (THF, 40~mL) was slowly added. 
Reaction mixture was stirred at room temperature overnight. The brown reaction mixture was quenched adding saturated aqueous ammonium chloride (\ce{NH4Cl}, 25~mL). 
Aqueous phase was extracted with di\-chloro\-methane (2 $\times$ 30~mL).
Residual iodine was quenched washing with saturated aqueous sodium thiosulfate (\ce{Na2S2O3}) then organic phase was dried on sodium sulfate (\ce{Na2SO4}), filtered and the solvent evaporated under reduced pressure. Flash column chromatography (silica, cyclohexane:toluene 49:1) produced 2-iodo-1-methoxy\-naphthalene \cmpd{moni} as a pale yellow oil (2.16~g, 7.60~mmol, yield 40~\%). $\mathbf{^{1}}$\textbf{H-NMR} (300~MHz, \ce{CDCl3}, 
Figure \ref{sp:moni}, $\delta$, ppm):  8.21 (d, J = 7.7~Hz, 1H, 2-CH), 7.82 (m,  2H, 5-CH, 8-CH), 7.63 – 7.50 (m, 2H, 3-CH, 4-CH), 7.33 (d, J = 8.7~Hz, 1H, 7-CH), 4.03 (s, 3H, 12-CH$_3$O). $^\mathbf{13}$\textbf{C-NMR} (75~MHz, \ce{CDCl3}, $\delta$, ppm):  156.0, 134.7, 134.3, 127.9, 127.7, 126.4, 126.3, 125.4, 121.8, 87.1, 61.2.


\subsection{Palladium Catalyzed Homocoupling of 2-iodo-1-methoxy\-naphthalene \cmpd+{moni}}\label{sec:sperimentale-schifo}
In a three necked flask under a nitrogen atmosphere 2-iodo-1-methoxy\-naphthalene \cmpd{moni}, 2.16~g, 7.60~mmol) was added to bis(di\-benzyl\-idene\-acetone)\-palladium (\ce{Pd(dba)2}, 0.44~g, 0.77~mmol) and caesium fluoride (CsF, deliquescent, 11.52~g, 75.84~mmol) in dimethylformamide (DMF, 75~mL). Reaction mixture was stirred for 18 hours at \SI{90}{\celsius} and monitored by TLC (toluene\-:hexane 1:1). The reaction was quenched pouring water (0.5~L) and extracted with diethyl ether (4 $\times$ 100~mL). The organic fraction was dried on sodium sulfate (\ce{Na2SO4}), filtered, 
the solvent evaporated to produce a viscous red-brown liquid. Product was filtrated through a short silica column and purified using a flash column chromatography (silica, toluene\-:hexane 1:1) to obtain an unexpected product: 8-(1-methoxy-2-naphthalenyl)-2H-naphtho[1,8-bc]furan (\cmpd{schifo}, 0.4812~g, 1.541~mmol, yield 20.3~\%) instead of the product of coupling 1,1'-dimethoxy-2,2'-bi\-naphthalene \cmpd{dmon}. $\mathbf{^{13}}$\textbf{C-NMR} (75~MHz, \ce{CDCl3}, $\delta$, ppm):  159.0, 153.8, 139.2, 134.5, 132.2, 131.5, 129.1, 128.8, 128.7, 127.9, 126.3, 126.1, 125.1, 123.8, 123.0, 122.7, 115.9, 115.6, 112.7, 77.5, 61.5, 61.5.

\subsection{1,1'-di\-hydroxy-2,2'-bi\-naphthalene \cmpd+{dhn}}\label{sub:sperimentale-dhn}
% Abbiamo messo il BBr3 ed è venuta una grandissima schifezza paurosa: un polimero.

Using a Luer-Lock siringe boron tribromide (\ce{BBr3}, 0.7~mL, 2~g, 7~mmol) was added to a solution of 1,1'-di\-meth\-oxy-2,2'-bi\-naphthalene \cmpd{dmon}, 0.7958~g, 2.531~mmol) in di\-chloro\-methane (9~mL) at \SI{0}{\celsius} under nitrogen atmosphere. Then the reaction was stirred at room temperature overnight. The reaction was quenched by the dropwise addition of water (20~mL) and the aqueous layer was extracted with di\-chloro\-methane (5 $\times$ 20~mL). The combined organic layers were washed with brine, dried over sodium sulfate, filtered and concentrated using rotary evaporator. 
The obtained product was identified using TLC (toluene\-:hexane 4:1) as pure 1,1'-di\-hydroxy-2,2'-bi\-naphthalene (\cmpd{dhn}, 0.7227~g, 2.524~mmol, yield 100~\%). $\mathbf{^{1}}$\textbf{H-NMR} (300~MHz, \ce{CDCl3}, Figure \ref{sp:dhn}, $\delta$, ppm):  8.40 – 8.31 (m, 2H, 2-CH, 20-CH), 7.93 – 7.85 (m, 2H, 5-CH, 17-CH), 7.64 – 7.53 (m, 6H, 3-CH, 4-CH%, 7-CH, 15-CH  non si riesce a giustificare
, 18-CH, 19-CH, unassigned), 7.40 (d, J = 8.4~Hz, unassigned%, 2H, 8-CH, 14-CH non si riesce a giustificare
). $\mathbf{^{13}}$\textbf{C-NMR} (75~MHz, \ce{CDCl3}, $\delta$, ppm):  149.2, 134.9, 128.1, 127.8, 127.2, 126.1, 124.7, 122.6, 121.5, 115.8.

\subsection{\legante{} \cmpd+{legante}}
%porco schifo che nomenclatura dergaazzo: 1,2-d:2',1'-f vuol dire che sul lato numero d del ciclo OPOCCCC c'è fissato nell'ordine l'atomo 1 e il 2 di un naftile, poi i : fanno da spaziatore e si dice che 2' e 1' cioè gli atomi dell'altro naftile sono fusi al lato f della diossafosfefina o come si chiama.

%[3$\alpha$-acetyloxy-12$\alpha$-5$\beta$-cholan-12$\alpha$-yl]oxy]-2,2'-bi\-naphthyl-1,1'-diyl dioxaphosphepin, BOOOOOH 18-[[2'-(diphenylphosphino)[1,1'-bi\-naphthalen]-2-yl]oxy]-
%-phosphite3$\alpha$-acetilossi-12$\alpha$(2,2'-binaftil-1,1'-diilil)-fosfito-\\7-deossicolato di metile]{3$\alpha$-acetilossi-12$\alpha$(2,2'-binaftil-1,1'-diilil)-fosfito-7-deossicolato di metile}

%uguale ma con i binaftili legati in modo più normale atropos 

%4-chlorodinaphtho[1,2-d:2',1'-f][1,3,2]dioxaphosphepin

%Dinaphtho[1,2-d:2',1'-f][1,3,2]dioxaphosphepin

A solution of 1,1'-di\-hydroxy-2,2'-bi\-naphthalene \cmpd{dhn}, 0.6212~g, 2.170~mmol) in anhydrous toluene (30~mL) was added dropwise to a mixture of phosphorus trichloride (\ce{PCl3}, 0.2~mL%volume estratto dagli appunti di lab di Anila (ho fatto questo passaggio con con loro)
, 0.3~g, 2~mmol), toluene (4~mL) and triethylamine (\ce{Et3N}, 0.6~mL, 0.4~g, 4~mmol) at \SI{0}{\celsius} under nitrogen atmosphere. After 3 hours of stirring at room temperature the reaction mixture was filtered under nitrogen atmosphere (using a filtering tube with sintered glass disc, sealed in centre, porosity G-3) and poured dropwise 
into a solution of 3$\alpha$-acetyloxy-12$\alpha$-hydroxy-7-deoxy\-cholic acid methyl ester \cmpd{amda}, 1.57~g, 3.50~mmol) and 4-dimethylaminopyridine (DMAP, 0.25~g, 2.1~mmol) in toluene (15~mL) and triethylamine (\ce{Et3N}, 0.6~mL, 0.4~g, 4~mmol). The reaction mixture was heated at reflux %(140°C) ma il toluene bolle a 110°C... boh...
and stirred overnight. Then was filtered through a sintered glass filter, the solvent was evaporated and the mixture was purified using two flash column chromatographies  
(silica, di\-chloro\-methane:acetone 49:1; silica, di\-chloro\-methane:acetone 99:1) to afford pure \legante{} %(3$\alpha$,5$\beta$,12$\alpha$)-3-(acetyloxy)-12-[dinaphtho[1,2-d:2',1'-f][1,3,2]dioxa\-phosphepin-14-yloxy]-cholan-24-oic acid methyl ester
 (\cmpd{legante}, 83.4~mg, 0.109~mmol, yield 5~\%).
$\mathbf{^{1}}$\textbf{H-NMR} (300~MHz, benzene-d6, Figure \ref{sp:legante}, $\delta$, ppm):  8.54 (dd, J = 26.3, 8.2~Hz, 2H, 47, 54-CH), 7.69 – 7.27 (m, 10H, 36, 37, 46, 48, 49, 42, 43, 51, 53, 55-CH), 4.71 - 4.61 (m, 2H, 12-CHCCO, 3-CHCCO), 3.40 (s, 3H, 29-\ce{CH3O}), 1.64 (s, 3H, 31-\ce{CH3COO}), 2.33 – 0.41 (m, 29H), 0.92 (d, J = 6.1~Hz, 3H, 22-\ce{CH3}), 0.70 (s, 3H, \ce{CH3}), 0.49 (s, 3H, \ce{CH3}).


%nmr t variabile fatti in toluene

\subsection{(2-nitro-cyclo\-hexyl)benzene \cmpd+{ncb}}

Under nitrogen atmosphere \ce{[RhCl(C2H4)2]2} (6.2~mg, \SI{16}{\micro\mole}) and \legante{}%(3$\alpha$,\-5$\beta$,\-12$\alpha$)-3-(acetyloxy)-12-[di\-naphtho[1,2-d:2',1'-f][1,3,2]di\-oxa\-phosphepin-14-yl\-oxy]-cholan-24-oic acid methyl ester
(\cmpd{legante}, 48~mg, \SI{63}{\micro\mole}) were introduced in a Schlenk tube and vacuum-nitrogen cycles were performed. Toluene (2.5~mL) was poured in the flask and the mixture was stirred for half an hour. Potassium hydroxyde (KOH, 31~mg, 0.54~mmol) in water (0.25~mL, deoxygenated bubbling \ce{N2}
 %bubbled with \ce{N2} in order to remove oxygen
) was added and the mixture was stirred for 10 minutes. Finally, phenyl\-boronic acid \cmpd{pba}, 244~mg, 2.00~mmol) and 1-nitro\-cyclo\-hexene (\cmpd{nc}, 0.12~mL, 0.14~g, 1.1~mmol) were added. 
The whole reaction mixture was stirred at \SI{65}{\celsius} for 24 hours. Then the reaction mixture was extracted with methyl acetate (3 $\times$ 10~mL). The combined organic phases were washed with a saturated aqueous solution of sodium bi\-carbonate (\ce{NaHCO3}) and with brine.% (NaCl, aqueous, saturated). 
Then was dried on sodium sulfate and filtered. A mixture of 4 diastereoisomers of (2-nitro-cyclo\-hexyl)benzene \cmpd+{ncb} were obtained. According to GC-FID (Figure \ref{sp:gc}) the conversion was 17~\% (peak area of \emph{cis} and \emph{trans} together divided by the peak area of unmodified precursor) and the \emph{cis}/\emph{trans} diastereo\-meric excess was 25~\% with a majority of \emph{trans} diastereomer. Product was purified with a column chromatography (silica, \n-hexane:ethyl acetate 20:1, bad separation). Then the \emph{trans} product was analyzed by chiral HPLC (Figure \ref{sp:hplc}, Lux\textsuperscript{\textregistered} Cellulose-1, cellulose tris (3,5-dimethyl\-phenyl\-carbamate) coated on \SI{5}{\micro\meter} silica-gel, normal phase, \n-hexane:isopropyl alcohol 95:5, flux 1~mL/min, column heated \SI{60}{\celsius}, wavelength 220~nm) revealing 60~\% enantio\-meric excess. 